Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_Appendix_A.Rmd
update html

mycols <- c("black", "blue", "purple")
#create density plots
curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.3),
      from=0, to=max.x,
      col=mycols[1],
      main = 'Log Normally distributed movement rates for three populations', #add title
      ylab = 'Density', #change y-axis label
      )

>>>>

mycols <- c("red", "green", "blue")
#create density plots
curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.3),
      from=0, to=max.x,
      col=mycols[1],
      main = 'Log Normally distributed movement rates for three populations', #add title
      ylab = 'Density', #change y-axis label
      )
